\documentclass[twoside]{article}
\usepackage[paperwidth=5.5in, paperheight=8.5in]{geometry}
\usepackage{fullpage}
\author{Stuart and Kate}
\title{Wedding Ceremony}
\date{14 April 2013}

\begin{document}
  \maketitle
  
  \section{Prelude - Brass Quintet}
    \begin{description}
      \item[\textbf{Gabrieli:}] Canzon per sonare 2
      \item[\textbf{Bozza:}] Sonatine
      \item[\textbf{Arutunian:}] Armenian Dances
    \end{description}
    \subsection{Stuart/Luise enter}
    
  \section{Ceremony}
    \begin{description}
      \item[\textbf{Stravinsky:}] Fanfare for a New Theatre
    \end{description}
  
  	\begin{center}
      \textbf{Stuart}
    \end{center}
Hello Everyone! For those of you who don’t know me, I’m Stuart (the groom...). For those of you who don’t know Kate she (points to Luise) isn’t her. I feel like I’ve been married to Kate for about 2.5 years; ever since we started sharing our lives, and our apartment, in Boston. The State of Massachusetts recognized our marriage a month ago, on Pi Day. Today we are inviting you: friends, family, friends of family, and family of friends, to witness our commitment, and hope, that those of you who don’t know us (and those of you who think you know us) can learn something of who we are. Please join me in standing, and waiting, for Kate.
		
    \subsection{Wedding party enters}
      \begin{description}
        \item[\textbf{Mussorgsky:}] Promenade from Pictures at an Exhibition
      \end{description}
  		
      Bride Enters
  		
      Quick Kiss
	  
    \subsection{Parents} 
     
     Bride invites parents to front
     
     Parents bind our hands

  	\subsection{Readings:}

      \begin{center}
        \textbf{Adam}
      \end{center}
      \begin{quote}
        When a man cannot choose, he ceases to be a man.
        ― Anthony Burgess, A Clockwork Orange
      \end{quote}

We believe that marriage is a choice. As a society, we have dispensed with marriage as a tool for social or financial advancement, for the transfer of wealth, the resolution of familial and political disputes, and the satisfaction of religion. The choice to be married at all, the choice to marry a particular person, these are choices made by individuals of free will and without coercion. 

      \begin{center}
        \textbf{Marina}
      \end{center}
      \begin{quote}
        In this galaxy there’s a mathematical probability of three million Earth-type planets. And in the universe, three million million galaxies like this. And in all that, and perhaps more...only one of each of us.
        --Dr. McCoy, Star Trek, “Balance of Terror”
      \end{quote}

If we are each destined to find a particular soul mate who lives at the same time as us, within a few years of our age, there are approximately five hundred million potential people to sort through, and we will only make eye contact with about Fifty Thousand of them in our lifetime. Average odds there: one in ten-thousand. 

So unless most of us are faking it, love itself has an element of choice. The journey from meeting a person to loving a person involves millions of choices: when to adapt and when to remain resolute, when to be vulnerable and when to be strong, when to compromise. Once we discover that we are, in fact, in love, the most important choice of all is whether to maintain it. 
	
        \begin{center}
          \textbf{Luise}
        \end{center}
        \begin{quote}
          Someone once told me that time was a predator that stalked us all our lives. I rather believe that time is a companion who goes with us on the journey and reminds us to cherish every moment, because it will never come again. What we leave behind is not as important as how we've lived. After all Number One, we're only mortal. 
          -- Picard; Star Trek: Generations
        \end{quote}
        
We each have a finite time, and choosing to share that time is choosing to risk a person’s most precious resource. When two people commit to sharing the remainder of their time, they do so in the hope that they can each contribute something to that shared experience that the other would lack alone. This commitment is not made merely for companionship, which can be had in much smaller, safer, parcels, but for growth and adventure. For the life that would not be lived by a person alone. 

        \begin{center}
          \textbf{Meg}
        \end{center}
        \begin{quote}
          ``But I don't want comfort. I want God, I want poetry, I want real danger, I want freedom, I want goodness, I want sin.''
          ``In fact,' said Mustapha Mond, you're claiming the right to be unhappy.''
          ``All right then,'' said the Savage defiantly, ``I'm claiming the right to be unhappy.'' 
          ``Not to mention the right to grow old and ugly and impotent; the right to have syphilis and cancer; the right to have too little to eat; the right to be lousy; the right to live in constant apprehension of what may happen tomorrow; the right to catch typhoid; the right to be tortured by unspeakable pains of every kind.'' 
          There was a long silence. ``I claim them all,'' said the Savage at last.
          Mustapha Mond shrugged his shoulders. ``You're welcome,'' he said.
          -― Aldous Huxley, Brave New World
        \end{quote}
        
This commitment is made not to be safe, or stable, but challenge and grow and explore. Complementary impetus and complementary experience are combined in this to yield possibilities that exceed what any one person can do. 
 
        \begin{center}
          \textbf{Marina}
        \end{center}
        \begin{quote} 
          If you can't take a little bloody nose, maybe you oughtta go back home and crawl under your bed. It's not safe out here. It's wondrous, with treasures to satiate desires both subtle and gross; but it's not for the timid.
          -- Q (Q Who?)
        \end{quote}

        \begin{center}
          \textbf{Adam}
        \end{center}

It is in this spirit of adventure and growth, of love and choice, that Stuart and Kate commit today to share their lives. To explore strange new worlds. And to boldly go where neither had gone before.

      \subsection{Bernstein: Make Our Garden Grow}
        \begin{center}
         \textbf{String Quartet + Soprano + Tenor}
        \end{center}

  	   \subsection{Vows}
         \begin{center}
           \textbf{Stuart}
         \end{center}
          
I, Stuart, take you, Kate, to be my wife. To have and to hold, for richer and for poorer, in sickness and in health, from this day forth as long as we both do live. I promise to be patient, to remain independent, and to communicate to the fullest and best of my ability. I will love and honor you all the days of my life.
	
          \begin{center}
           \textbf{Kate}
          \end{center}
          
I, Kate, take you, Stuart, to be my husband. To have and to hold, for richer and for poorer, in sickness and in health, from this day forth as long as we both do live. I promise to be patient, to remain independent, and to communicate to the fullest and best of my ability. I will love and honor you all the days of my life.

  	   \subsection{Rings}
         \begin{itemize}
           \item Luise holds Kate's ring for Stuart
           \item Meg holds Stuart's ring for Kate
         \end{itemize}
          
         \begin{center}
           \textbf{Someone}
         \end{center}
         \begin{quote}
  		     [Two] Ring[s] to rule them all, [Two] Ring[s] to find them,
  [Two] Ring[s] to bring them all and in [the presence of these witnesses] bind them
  	        -- JRR Tolkien
         \end{quote}

          \begin{center}
          \textbf{Kate}
          \end{center}
  		    With this ring, I thee wed.
          \begin{center}
          \textbf{Stuart}
          \end{center}
          With this ring, I wed thee!
          \begin{center}
          \textbf{Kate and Stuart}
          \end{center}
          Kiss!
          
  	   \subsection{Recessional - Bach: Contrapunctus IX}
         \begin{center}
           \textbf{Brass Quintet}
         \end{center}

  \section{Cocktail Hour - String Quartet}
    \begin{enumerate}
    	\item Brass Quintet, Soprano, Tenor dismissed
    	\item String Quartet moves to cocktail hour location
    	\item Guests move to Cocktail Hour
    	\item Bride, Groom, Wedding Party, and close family take pictures
    	\item Party and family return to cocktail hour; Bride and Groom have some quiet time
    \end{enumerate}
    
  \section{Reception}
    \begin{enumerate}
      \item Guests move to Reception
      \item Lunch Served
      \item Someone: Announces Kate and Stuart
      \item Toasts
      \item Cake
    \end{enumerate}

  \section{End}
    
\end{document}
